When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
replaced calls with values in pilot section

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
All results are detailed in the Supplementary Material.

@@

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
Of the $N=$ participants who filled out the online questionnaires, $n=$ came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=$ participants.

>>>>

The sample of the pilot study consisted of $N=15$ participants (53.3% female, $M=24.43$ ($SD=3.59$) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
All results are detailed in the Supplementary Material.

@@

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r length(datalist_nback)`$ came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=`r nrow(data_quest)`$ participants.
